Compiling refinement types to dependent types

### 2020-07-02 tex/paper.tex
Start playing around with ott/ottalt
More syntax defined
Try to fit the syntax in two subfigures
Start working on defining typing rules
Finally got the T-App rule to typecheck
ott is fun!
Add a refinement variable metavariable
Adding arrows is trivial now
WFT → TFW as a nicer abbreviation
Add lambda abstraction typing rule
Stub conditionals
Start working on the subtyping rules
Get rid of the binops for the core language
Add the TWF-BaseRef rule
Add the T-Sub rule
Rename BaseRef → TrueRef
Add TWF-Conj rule
Move \top to the term level, add \bot and add typing rules
Disambiguate surface language

\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}

@@

\section{Calculus definition}

@@

@@

>>>>

\documentclass[a4paper]{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage{amsmath,amsfonts}
\usepackage{xcolor}
\usepackage{ottalt}
\usepackage{subcaption}

\addtolength{\topmargin}{-1.75in}
\addtolength{\textheight}{2.75in}

\newNTclass{nonterm}
\newnonterm e \varepsilon
\newnonterm{eS}{\varepsilon}
\newnonterm{ec}{\overline\varepsilon}
\newnonterm r \rho
\newnonterm{tS}{\tau}
\newnonterm{tC}{\overline\tau}
\newnonterm s s
\newnonterm B B
\newnonterm{G}{\Gamma}
\newnonterm{GC}{\overline\Gamma}
\newnonterm{binop}{\odot}

\newNTclass{gterm}
\newgterm x x
\newgterm v v
\newgterm n n

\inputott{surface.ott}

@@

\section{Calculi definitions}

@@

\begin{figure}[ht]
  \footnotesize
  \begin{subfigure}{.6\textwidth}
	\nonterms{eS}
	\caption{Term level}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
	\nonterms{r,B,tS}
	\caption{Type level}
  \end{subfigure}
  \caption{Surface language syntax}
  \label{fig:surface_syntax}
\end{figure}

\begin{figure}[ht]
  \footnotesize
  \drules[TWF]{$\nonterm G \vdash \nonterm{tS} \text{ ok}$}{type well-formedness}{TrueRef,Base,Conj,Arr}
  \drules[T]{$\nonterm G \vdash \nonterm{eS} : \nonterm{tS}$}{term typing}{BoolTop,BoolBot,Var,Abs,App,If,Sub}
  \drules[ST]{$\nonterm G \vdash \nonterm{tS}_1 <: \nonterm{tS}_2$}{subtyping}{Base,Arr}
  \caption{Surface language typing rules}
  \label{fig:surface_typing}
\end{figure}

@@

\begin{figure}[ht]
  \footnotesize
  \nonterms{ec,s}
  \caption{Core language syntax}
  \label{fig:core_syntax}
\end{figure}

\begin{figure}[ht]
  \footnotesize
  \drules[CT]{$\nonterm G \vdash \nonterm{ec}_1 : \nonterm{ec}_2$}{core typing}{Sort,Var,Weaken,Form,App,Abs,Conv}
  \caption{Core language typing rules}
  \label{fig:surface_typing}
\end{figure}
